---
title: Bibliography Management - in construction
author: IJ
date: '2019-11-29'
slug: bibliography-management
categories:
  - R
tags:
  - Rmarkdown
subtitle: ''
summary: ''
authors: []
lastmod: '2019-11-29T11:57:03+01:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
link-citations: yes
references:
- id: xie2016bookdown
  title: 'Bookdown: Authoring Books and Technical Documents with R Markdown'
  author: 
  - family: 'Xie'
    given: 'Yihui'
  publisher: 'CRC Press'
  type: book
  issued:
    year: '2016'
---

Citation, references and bibliography may take some times. Especially if you do not anticipate that.

Here are some tricks or solutions I have found for specific challenges and situations during the conversion of my materials into another type using R.


## Referencing in Rmd

Quite simple, evenif you do not master BibTeX.

You need a BibTeX file, with extension `.bib`. For example a file with two references:

```
@article{RCoreTeam,
  Title   = {R: A Language and Environment for Statistical Computing},
  Author  = {{R Core Team}},
  Year    = {2015},
  Type    = {Journal Article},
  Url     = {http://www.R-project.org}
} 
@book{xie2016bookdown,
  title={Bookdown: Authoring Books and Technical Documents with R Markdown},
  author={Xie, Yihui},
  year={2016},
  publisher={CRC Press}
}
``` 

In the YAML of you document after the output definition you add :

```{r, eval=FALSE}
output: pdf_document
bibliography: [Liste_Publi1.bib]
link-citations: yes
nocite: '@*'
```

- `bibliography:` indicating the `.bib` file or files : `[Liste_Publi1.bib, Liste_Publi2.bib]`
- `link-citations: yes`: to make each citation linked to the reference in the bibliography section.
- `nocite: '@*'`: where `'@*'` is for all references in the bib file. You can choose specific reference that are not cited in the text, but that you want appear in the bibliography :
```{r, eval=FALSE}
nocite: |
  @item1, @item2
```

Finaly in your text, you add citation using `@xie2016bookdown` or `[@xie2016bookdown]` to abtain a citation without or with parentheses (  @xie2016bookdown or [@xie2016bookdown] ).


## Transforming a text references list into a bibtex bibliography

**Objective:** Transform my 90 references list into a BibTeX file.

I use [text2bib](https://text2bib.economics.utoronto.ca/index.php/index/convert) free online tool, developped and maintained at Toronto University by Martin J. Osborne and Fabian Qifei Bai.

+ It requires to sign up for a count, but is free and non intrusive (until now).
+ Recognition of the fields is partial (75%). Efficient for publication in journal and books, merely for inbook publication. For conferences, working paper, etc, some files have to be corrected (mainly copy-paste containt of erroneous fields to the correct one)
+ The limitation of **text2bib** is that you can not (or I do not find how to) change the proposed reference type when inappropriate (ex from `@article` to `@inbook`)

The step by step approach:

- step 1: upload the `.txt` file of your references list. In this file, each line is a standardized reference. References/lines are separated by blank line (return)  
- step 2: a interface display the proposed bibtex data with precompletion of each field (author, year, journal, etc.).

- step 3: once you have checked a reference, you validate with  `Add item to BibTeX file and continue`

- step 4: once you have checked all references (I have done 90 in less than 1 hour), click  `Display current BibTeX file (in new window)`  or  `Save current BibTeX file `, to view or save the bibtex file agregating your checked references.


Finally I create a rmd file containing all the references (see section above)


## Sources:

- the classic [RStudio documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html)
- [Text2Bib website](https://text2bib.economics.utoronto.ca/index.php/index/convert)
