---
title: 'My Publications List'
author: I Joly
date: '2020-02-20'
slug: journal
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-02-20'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
bibliography: data/Liste_Publi3.bib 
---

# My Publications List
performed with `RefManageR` package

# Recent Publications (* HCERES ranking)

```{r setup, include = FALSE, cache = FALSE}
library(RefManageR)
#bib <- ReadBib(system.file("Bib", "biblatexExamples.bib", 
#                           package = "RefManageR"), check = FALSE)
myBib <- ReadBib("data/Liste_Publi3_enc.bib", check = FALSE)
bib2 <- myBib[[seq_len(5)]]
BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear",
           bib.style = "numeric")
```


`r NoCite(bib = myBib, author = "Joly")`


**References**

```{r results = "asis", echo = FALSE}
PrintBibliography(myBib[[1:15]], .opts = list(check.entries = FALSE, sorting = "ydn"))
```

**More References**

```{r results = "asis", echo = FALSE}
PrintBibliography(myBib[[16:17]])
```

**Chapitres**
```{r results = "asis", echo = FALSE}
PrintBibliography(myBib[[18:10]])
```

**Sources**

- great [RefManageR] (https://github.com/ropensci/RefManageR) packages by Mathew W. McLean

## Publications list on HAL

Accès à la liste de mes [publications sur HAL]([HAL](https://haltools.archives-ouvertes.fr/Public/afficheRequetePubli.php?auteur_exp=iraga%C3%ABl+Joly&CB_auteur=oui&CB_titre=oui&CB_article=oui&langue=Anglais&tri_exp=annee_publi&tri_exp2=typdoc&tri_exp3=date_publi&ordre_aff=TA&Fen=Aff&css=../css/VisuRubriqueEncadre.css))

La liste de mes publications sur hal est réalisée à partir de [HAL-tools](https://haltools.archives-ouvertes.fr/)


## Other tools to be explored (one day...)

- [Lier les ID hal, orchid, etc](https://archibibscdf.hypotheses.org/997)


